---
title: "Questionnaire design"
format:
  html:
    toc: true
    css: justify.css
---

\[This section considers initially the questionnaire applied during the pilot study, and which could be modified in the actual implementation of the survey\]

The questionnaire has four sections:

1.  Informed consent
2.  Distributive-Conjoint experiment
3.  Attitudinal items
4.  Socio-economic characterization

Some characterization questions where introduced after the informed consent to monitor the quotas as well as to avoid jumping in quickly in the conjoint task, in order to give time to get used to the platform and the sense of the survey.

## Informed consent and ethics certification (@tomasurzuam)

## Distributive Conjoint-Survey experiment

This section describes the core element of the survey: the design and implementation of the distributive conjoint module. This module is based on a distributive design, which is a type of survey experiment that allows researchers to study how people allocate scarce resources among competing claimants. In this case, the scarce resource is a fixed scholarship fund, and the competing claimants are two applicants with different attributes. The design allows researchers to examine how respondents make trade-offs between different attributes of the applicants, such as their academic performance, financial need, and personal characteristics. In this case, the attributes of the applicants are operationalized based on the CARIN and recast NICER frameworks, which are widely used in the welfare deservingness literature. The design also allows researchers to test hypotheses about how different attributes of the applicants affect respondents' allocation decisions, and how these decisions are influenced by respondents' own characteristics and beliefs.

The design adapts the Distributional Survey Experiment of @gilgen_disentangling_2022 to a conjoint format [@hainmueller_causal_2014], combining the tabular presentation and complete, independent randomization of a conjoint experiment with the fixed-sum allocation task characteristic of distributive designs. The applicant attributes operationalize deservingness criteria drawn from the welfare deservingness literature, specifically the CARIN and recast NICER frameworks [@oorschot_who_2000; @meuleman_welfare_2020; @knotz_recast_2022]; the theoretical rationale for each attribute, the derivation of the hypotheses, and the analysis plan are documented separately in the [Pre Analysis Plan](https://jus-mer.github.io/survey-jusmer/surveys/conjoint-test/design/conjoint-preplan.html).

This section is organized in the following subsections:

1.  Task design and randomization
2.  Analysis considerations
3.  Power analysis

### Task design and randomization

The study uses a **paired-profile distributive conjoint**, a design that fuses the randomization logic of conjoint survey experiments with the allocative logic of distributive justice experiments. As in a standard conjoint, each task presents two profiles whose attributes are independently randomized, and the analysis recovers the effect of each attribute and level on the outcome. What departs from the standard conjoint is the response: rather than choosing one profile over the other, the respondent distributes a fixed resource between them, allocating a percentage of the total to each. The design therefore functions as an *allocator*—it asks how a scarce good should be divided between two independent claimants—and reveals the weight respondents place on each attribute through the share they are willing to grant.

**Attributes and levels {#sec-attributes}**

The profiles are defined by seven attributes, which operationalize six deservingness criteria (need, identity, control, effort, reciprocity, and attitude), and one additional attribute (sex of the applicant). Two of the deservingness criteria are operationalized with three levels, while the remaining four are operationalized with two levels.

+-----------------+-------------------------------+------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------+
| Attribute       | Criterion                     | Profile label                                              | Levels                                                                                                          |
+:================+:==============================+:===========================================================+:================================================================================================================+
| **Need**        | Need (CARIN/NICER)            | Makes ends meet with *(Su hogar llega a fin de mes con:)*  | 1 Comfort *(Holgura)*\                                                                                          |
|                 |                               |                                                            | 2 Hardship *(Dificultad)*                                                                                       |
+-----------------+-------------------------------+------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------+
| **Identity**    | Identity (CARIN/NICER)        | Country of birth *(País de nacimiento:)*                   | 1 Chile\                                                                                                        |
|                 |                               |                                                            | 2 Peru *(Perú)*\                                                                                                |
|                 |                               |                                                            | 3 Venezuela                                                                                                     |
+-----------------+-------------------------------+------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------+
| **Control**     | Control (CARIN/NICER)         | Needs the scholarship because *(Requiere la beca porque:)* | 1 Did not apply to other scholarships in time *(No alcanzó a postular a tiempo a otras becas)*\                 |
|                 |                               |                                                            | 2 Applied to other scholarships but received no funding *(Postuló a otras becas pero no obtuvo financiamiento)* |
+-----------------+-------------------------------+------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------+
| **Effort**      | Effort (NICER)                | Studies *(Estudia:)*                                       | 1 Less than their peers *(Menos que sus compañeros)*\                                                           |
|                 |                               |                                                            | 2 The same as their peers *(Igual que sus compañeros)*\                                                         |
|                 |                               |                                                            | 3 More than their peers *(Más que sus compañeros)*                                                              |
+-----------------+-------------------------------+------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------+
| **Reciprocity** | Reciprocity (CARIN/NICER)     | Outside their studies *(Fuera de sus estudios:)*           | 1 Has not done volunteer work *(No ha hecho voluntariado)*\                                                     |
|                 |                               |                                                            | 2 Has done volunteer work *(Ha hecho voluntariado)*                                                             |
+-----------------+-------------------------------+------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------+
| **Attitude**    | Attitude (CARIN)              | Sees the scholarship as *(Ve la beca como:)*               | 1 Something they deserve *(Algo que se merece)*\                                                                |
|                 |                               |                                                            | 2 Help they are grateful for *(Una ayuda que agradece)*                                                         |
+-----------------+-------------------------------+------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------+
| **Sex**         | Ascriptive (signaled by name) | First name (no explicit row)                               | 1 Male name\                                                                                                    |
|                 |                               |                                                            | 2 Female name                                                                                                   |
+-----------------+-------------------------------+------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------+

<p style="font-size:0.8rem; color:#555; margin-top:0.8rem;">

The resulting profiles are presented in a tabular format, with each attribute and its corresponding level displayed in a separate row. The table is designed to be visually clear and easy to read, allowing respondents to quickly compare the two profiles and make their allocation decisions. Besides, the allocation task is performed with a slider that allows respondents to allocate a percentage of the total scholarship fund to each profile, with the constraint that the total allocation must equal 100%. The slider is designed to be intuitive and user-friendly, allowing respondents to easily adjust their allocations and see the resulting changes in real-time.

```{=html}
<iframe src="images/survey.html" width="100%" height="800" frameborder="0" style="border: none; background: #ffffff; opacity: 1; filter: none; mix-blend-mode: normal;"></iframe>
```

-\> link to pre-pilot survey (allows translation in chrome): <https://jus-mer-pre-piloto-v2.share.connect.posit.cloud>

### Tasks allocation and randomization

Considering the number of attributes and levels, the total number of possible profiles is (2x3x2x3x2x2x2) = 288. The total number of possible (non redundant) profile pairs is p*(p-1)/2 = (288*287)/2 = 41,328. The survey design randomly selects a subset of these pairs to present to respondents, ensuring that each respondent sees a unique combination of profiles.

The experiment uses complete and independent randomization of attribute levels, the reference case in Hainmueller et al. [-@hainmueller_causal_2014] and the default for most applied conjoint designs [@bansak_conjoint_2021]. For each profile $(j)$, every attribute is drawn independently of the others and of the competing profile, with uniform probability within its attribute ($1/2$ for the four two-level attributes, $1/3$ for Effort and Identity). No attribute is conditioned on another and no level is reweighted, so the joint distribution of profiles is the product of the attribute marginals [@hainmueller_causal_2014]. Randomization occurs at the profile level and is performed anew for each respondent and task, rather than as a fixed block assigned in advance. Under this scheme the assignment of each attribute is by construction independent of the potential outcomes, which is the condition that identifies the AMCEs [@hainmueller_causal_2014]. The randomization is implemented in the survey platform using a custom script that generates the profiles and their corresponding levels on the fly, ensuring that each respondent sees a unique set of profiles.

A direct consequence of independent randomization is orthogonality: across the sample, the level of any one attribute is statistically independent of the level of every other, so the estimated effect of one attribute cannot be biased by the distribution of another. Exact zero correlation holds only in expectation, so it is worth stating what "independent" means at a finite sample. With 54,000 profiles the sampling standard error of a correlation between any two attribute indicators is approximately $1/\sqrt{54{,}000} \approx 0.004$, so inter-attribute correlations should fall within roughly $\pm 0.013$ of zero (three standard errors) purely by sampling variation. A simulation of the design under the realized sample size confirms this directly: across the full attribute set the largest observed within-profile correlation is $0.011$, within the expected band and stable across repeated seeds (see @sec-random-check). Departures of this magnitude are sampling noise, not structural dependence, and bias no AMCE.

### Power analysis and sample size

Under the binary-outcome formula produced by @schuessler_power_2020, the number of respondents required to detect an effect of a given size follows

$$N \approx \frac{K}{2} \cdot \frac{(z_{1-\alpha/2} + z_{\kappa})^2}{\delta_1^2},$$

where $K$ is the number of levels of the attribute, $\delta_1$ the target effect, here 3pp (percentage points), the lower range of effects in the deservingness literature [@knotz_recast_2022; @gilgen_disentangling_2022], and the middle term equals 7.84 at the conventional $\alpha = 0.05$ and 80% power. Three-level attributes (Effort, Identity) are the demanding ones, because each of their contrasts uses only two-thirds of the profiles and so needs more respondents than a two-level attribute.

In the extant literature there are different proposal for determining the number of respondents, which usually include specific R packages and interactive tools (as cjpowR, cbcTools ...). in the appendix we provide a detailed comparison of alternatives for power analysis. For the final calculation we used the **cjpowR** package, which is a recent R package that provides functions for calculating the power of conjoint experiments based on the AMCE (in this case, 3pp or 0.03), attributes, and levels. 

```{r echo=TRUE}
library(cjpowR) # to install: devtools::install_github("m-freitag/cjpowR")
n_eff <- cjpowr_amce(amce = 0.03, power = 0.80, levels = 3)$n
n_profiles_per_task <- 2
n_tasks <- 5
n_respondents <- n_eff / (n_profiles_per_task * n_tasks) 
n_respondents
```

With this approach the minimun required sample size is **1,307** respondents. 

A different approach is to use a D-efficient design, which is a type of experimental design that maximizes the amount of information that can be obtained from a given number of respondents. D-efficient designs are often used in conjoint experiments to reduce the number of profiles that need to be presented to respondents while still allowing for the estimation of the main effects and interactions of interest. Using this approach, we can reduce the number of respondents needed to achieve the same level of statistical power.

As an exploratory check, we compare a D-optimal selection of profiles against the profiles that complete randomization would draw at the same sample size, restricted to main effects only (the estimand of interest here). At the profile level, using `AlgDesign::optFederov` (Fedorov algorithm, D-criterion) over the full 288-profile candidate set and the main-effects model `~ Need + Identity + Control + Effort + Reciprocity + Attitude + Sex`, we compute the D-efficiency of the optimal design against a benchmark of profiles drawn at random (200 repetitions per grid point) across a grid of sample sizes from 40 to 288 profiles.

```{r}
#| label: fig-deff-grid
#| fig-cap: "D-efficiency (main effects) of a D-optimal profile selection vs. complete randomization, across sample sizes"
#| echo: true
#| message: false
#| warning: false
library(AlgDesign)
library(ggplot2)
library(dplyr)

set.seed(20260922)

# Candidate set: every possible profile (the full 2x3x2x3x2x2x2 = 288 factorial),
# one row per profile, one column per attribute. This is the pool optFederov()
# will search over -- it cannot propose a profile that isn't in this list.
candidates <- gen.factorial(
  levels = c(2, 3, 2, 3, 2, 2, 2),
  varNames = c("Need", "Identity", "Control", "Effort", "Reciprocity", "Attitude", "Sex"),
  factors = "all"
)

# Model to optimize for: main effects only, no interactions (matches the
# confirmatory estimator in the Pre-Analysis Plan). model.matrix() turns the
# 7 factor columns into the dummy-coded design matrix X; p is its number of
# columns (parameters), needed to normalize the D-criterion below.
formula_main <- ~ Need + Identity + Control + Effort + Reciprocity + Attitude + Sex
X_full <- model.matrix(formula_main, data = candidates)
p <- ncol(X_full)

# Sample sizes to evaluate, from 40 profiles up to the full 288.
n_grid <- seq(40, 288, by = 10)
if (288 %% 10 != 0) n_grid <- unique(c(n_grid, 288))
# Number of random draws averaged per grid point, so the "complete
# randomization" benchmark isn't just one noisy draw.
n_random_reps <- 200

# For each candidate sample size N, compute two things and return them as a
# one-row data frame (lapply + bind_rows stacks these into one table):
results <- lapply(n_grid, function(n) {
  # (a) The D-optimal design of N profiles: optFederov searches the 288-row
  #     candidate set for the N-row subset (with replacement allowed) that
  #     maximizes det(X'X), i.e. is best for estimating the 7 main effects.
  #     nRepeats = 30 restarts the search from different random starting
  #     designs to avoid a local optimum.
  fed <- optFederov(
    frml = formula_main, data = candidates, nTrials = n,
    criterion = "D", nRepeats = 30, approximate = FALSE
  )
  Xopt <- model.matrix(formula_main, data = fed$design)
  # D-efficiency, scaled per observation: det(X'X)^(1/p) / n. This puts
  # designs of different N on a comparable footing -- it is the quantity
  # that (for a fixed target precision) trades off directly against N.
  d_opt <- det(t(Xopt) %*% Xopt)^(1 / p) / n

  # (b) The same quantity for N profiles drawn completely at random (with
  #     replacement, exactly as the survey's own randomization would do),
  #     repeated 200 times so we report its expected value rather than one
  #     lucky/unlucky draw.
  rand_deffs <- replicate(n_random_reps, {
    idx <- sample(nrow(candidates), n, replace = TRUE)
    Xr <- model.matrix(formula_main, data = candidates[idx, , drop = FALSE])
    detXtX <- det(t(Xr) %*% Xr)
    if (is.na(detXtX) || detXtX <= 0) NA_real_ else detXtX^(1 / p) / n
  })

  data.frame(N = n, D_optimal = d_opt, D_random = mean(rand_deffs, na.rm = TRUE))
}) |> bind_rows() |>
  # How much efficiency complete randomization is leaving on the table at
  # each N, in percentage terms.
  mutate(gain_pct = 100 * (D_optimal / D_random - 1))

# Plot both efficiency curves against N to see how quickly random catches up
# to the optimal design.
ggplot(results, aes(x = N)) +
  geom_line(aes(y = D_optimal, color = "D-optimal")) +
  geom_line(aes(y = D_random, color = "Complete randomization")) +
  labs(x = "Number of profiles", y = "D-efficiency (scaled)", color = NULL) +
  theme_minimal()
```

Walking through what the chunk does: it first builds the *candidate set* — every one of the 288 possible profiles — since `optFederov()` can only pick from profiles that exist in this list. It then fixes the *model* to optimize for, main effects only (`formula_main`), because efficiency is only meaningful relative to a specific set of parameters. For each sample size in the grid (40 to 288), it runs the Fedorov search to find the best N-profile subset for that model (`fed`, restarted 30 times to avoid local optima), and computes its per-observation D-efficiency (`d_opt`). It then computes the same statistic for N profiles drawn completely at random, repeated 200 times so the benchmark reflects the *expected* efficiency of randomization rather than one draw. Stacking one row per grid point (`bind_rows`) and adding the percentage gap (`gain_pct`) gives the `results` table plotted above.

Across the grid, the D-criterion of the optimal design is essentially flat (`r round(min(results$D_optimal), 4)`–`r round(max(results$D_optimal), 4)`) regardless of sample size, because with only seven main effects to estimate, the algorithm saturates the available information with very few distinct profiles. Complete randomization converges toward that optimum quickly: the efficiency gap is `r round(results$gain_pct[results$N == 40], 1)`% at N = 40 profiles, falls to `r round(results$gain_pct[results$N == 100], 1)`% by N = 100, and is only `r round(results$gain_pct[which.max(results$N)], 1)`% at the full 288-profile factorial. This is consistent with the argument made in the [Pre-Analysis Plan](https://jus-mer.github.io/survey-jusmer/surveys/conjoint-test/design/conjoint-preplan.html): given the small factorial space (288 profiles) and an estimand restricted to main effects, complete randomization is already close to D-optimal, and a formal D-efficient design offers, at most, a modest efficiency gain concentrated at small sample sizes — not a reduction large enough to justify replacing complete randomization, which also has the advantage of preserving marginal-based AMCE identification without fixing the profile set in advance.

**Back-of-envelope consequence for sample size.** Because $\text{Var}(\hat\beta) \propto \sigma^2(X'X)^{-1}$, the per-observation D-efficiency computed above trades off directly against N for a fixed target precision: to match the information of the randomized design at size $N_{\text{random}}$, the D-optimal design only needs $N_{\text{D-optimal}} \approx N_{\text{random}} / \text{ratio}$, where `ratio` is `D_optimal / D_random` at the relevant N. Applying this to the `r format(round(n_respondents), big.mark = ",")` respondents required above:


```{r}
#| label: tbl-deff-envelope
#| tbl-cap: "Back-of-envelope respondents implied by the D-efficiency gain, at selected profile-pool sizes"
#| echo: true
#| message: false
#| warning: false
envelope <- results |>
  filter(N %in% c(40, 100, 288)) |>
  mutate(
    ratio = D_optimal / D_random,
    respondents_random = round(n_respondents),
    respondents_D_optimal = round(n_respondents / ratio)
  ) |>
  select(N, ratio, respondents_random, respondents_D_optimal)

knitr::kable(
  envelope, digits = c(0, 3, 0, 0),
  col.names = c("Profile pool (N)", "Efficiency ratio", "Respondents (randomization)", "Respondents (D-optimal, implied)")
)
```

The implied saving tracks the efficiency gap directly: on the order of `r round(100 * (1 - 1/envelope$ratio[envelope$N == 40]))`% fewer respondents in the most favorable case (a small, 40-profile pool), shrinking to `r round(100 * (1 - 1/envelope$ratio[envelope$N == max(envelope$N)]))`% at the full 288-profile factorial — a few hundred respondents at most, not a change of order of magnitude. Two caveats apply. First, this is an approximation: the `r format(round(n_respondents), big.mark = ",")` baseline comes from `cjpowR`'s closed-form AMCE power formula [@schuessler_power_2020], derived under different assumptions (a Bernoulli-type outcome variance) than the linear-model D-efficiency computed here, so the two are not measuring precision on identical terms — the ratio is a reasonable order-of-magnitude translation, not an exact one. Second, it ignores the respondent fixed effects and cluster-robust standard errors used in the actual estimator (see Analysis considerations), which $(X'X)^{-1}$ alone does not capture. A precise answer would require a Monte Carlo power simulation — fitting the actual respondent-fixed-effects model with clustered SEs to data simulated under each design, across a grid of N — which in turn needs the outcome's residual variance and intra-respondent correlation. Neither is known yet; calibrating them is one of the stated purposes of the pilot, so a fully rigorous version of this exercise is deferred until pilot data are available.

**Pair-level check** 

The exercise above optimizes the *profile* pool, but the unit actually shown to respondents is a *task*: a pair of two profiles, subject to the restriction that they differ on at least two of the six CARIN/NICER attributes (see Implementation). Because the analysis model has no task-level term — each profile enters the regression as its own row, with only a respondent fixed effect — the information matrix $X'X$ of the full dataset is just the sum of the two profiles' individual contributions, regardless of which task paired them. In principle this means pairing does not, by itself, change D-efficiency; what can change it is the *restriction*, since it rules out some profile combinations and so shrinks the pool the design can be built from. `AlgDesign::optFederov` does not support this kind of restricted, two-row-per-task candidate set directly, so it is implemented here as a direct pair-level Fedorov-type exchange search: the candidate set is every admissible pair of profiles, and the algorithm swaps one task at a time for a better one whenever doing so raises $\det(X'X)$ of the full stacked design.

To enumerate the admissible pairs themselves — needed for the survey implementation, not just for the efficiency check — each attribute is now given its actual survey levels and labels, rather than the generic `1`, `2`, `3` codes used above: Need = dificultad (1) / holgura (2); Identity = chile (1) / venezuela (2) / peru (3); Control = aplico (1) / no aplico (2); Effort = mas (1) / igual (2) / menos (3); Reciprocity = hizo (1) / no hizo (2); Attitude = agradece (1) / merece (2); Sex = mujer (1) / hombre (2). This is a relabeling of the same seven factors, so it does not change the D-efficiency figures below (D-efficiency is invariant to which level is coded as the reference category); what it adds is a labeled candidate set from which the admissible pairs can be listed directly.

```{r}
#| label: fig-deff-pair-grid
#| fig-cap: "D-efficiency (main effects) of a D-optimal task selection vs. complete randomization under the pairing restriction, across sample sizes"
#| echo: true
#| message: false
#| warning: false
#| cache: true
library(AlgDesign)
library(ggplot2)
library(dplyr)
library(here)

set.seed(20260922)

# Candidate profiles, with each attribute's actual survey levels and labels
# (rather than generic 1/2/3 codes) so the admissible pairs below are
# directly readable/usable for implementation.
need_levels        <- c("dificultad", "holgura")        # 1, 2
identity_levels    <- c("chile", "venezuela", "peru")    # 1, 2, 3
control_levels     <- c("aplico", "no_aplico")            # 1, 2
effort_levels      <- c("mas", "igual", "menos")          # 1, 2, 3
reciprocity_levels <- c("hizo", "no_hizo")                # 1, 2
attitude_levels    <- c("agradece", "merece")             # 1, 2
sex_levels          <- c("mujer", "hombre")                # 1, 2

candidates <- expand.grid(
  Need        = factor(need_levels, levels = need_levels),
  Identity    = factor(identity_levels, levels = identity_levels),
  Control     = factor(control_levels, levels = control_levels),
  Effort      = factor(effort_levels, levels = effort_levels),
  Reciprocity = factor(reciprocity_levels, levels = reciprocity_levels),
  Attitude    = factor(attitude_levels, levels = attitude_levels),
  Sex         = factor(sex_levels, levels = sex_levels),
  KEEP.OUT.ATTRS = FALSE
)
formula_main <- ~ Need + Identity + Control + Effort + Reciprocity + Attitude + Sex
X_full <- model.matrix(formula_main, data = candidates)
p <- ncol(X_full)

# Admissibility matrix: TRUE for profile pairs (i, j) that differ on >= 2 of
# the 6 substantive (CARIN/NICER) attributes -- Sex is excluded, as in the
# actual survey check. admissible_idx lists every admissible pair once.
subst_attrs <- c("Need", "Identity", "Control", "Effort", "Reciprocity", "Attitude")
diff_count <- matrix(0L, nrow(candidates), nrow(candidates))
for (a in subst_attrs) diff_count <- diff_count + outer(candidates[[a]], candidates[[a]], FUN = "!=")
admissible_mat <- diff_count >= 2
diag(admissible_mat) <- FALSE
admissible_idx <- which(admissible_mat & upper.tri(admissible_mat), arr.ind = TRUE)
n_adm <- nrow(admissible_idx)
pct_admissible <- 100 * n_adm / choose(nrow(candidates), 2)

# Materialize every admissible pair as a labeled data frame -- one row per
# pair, attributes of profile A and profile B side by side -- and write it
# out for use in the survey implementation.
profileA <- candidates[admissible_idx[, 1], ]
names(profileA) <- paste0(names(profileA), "_A")
profileB <- candidates[admissible_idx[, 2], ]
names(profileB) <- paste0(names(profileB), "_B")
admissible_pairs_df <- cbind(pair_id = seq_len(n_adm), profileA, profileB)
rownames(admissible_pairs_df) <- NULL

out_dir <- here::here("..", "output", "conjoint-design")
dir.create(out_dir, recursive = TRUE, showWarnings = FALSE)
write.csv(admissible_pairs_df, file.path(out_dir, "admissible_pairs.csv"), row.names = FALSE)

# D-optimal search over n_tasks admissible pairs: starts from a random
# selection, then repeatedly tries replacing one task at a time with a
# random admissible candidate, keeping the swap only if it raises det(X'X)
# of the whole stacked (2*n_tasks-row) design. Restarted n_restarts times
# to avoid a local optimum, as optFederov's nRepeats does at the profile level.
doptimal_pairs <- function(n_tasks, n_restarts = 5, n_sweep = 3, n_try = 200) {
  best_det <- -Inf
  for (restart in seq_len(n_restarts)) {
    sel <- sample(n_adm, n_tasks, replace = TRUE)
    pairs <- admissible_idx[sel, , drop = FALSE]
    contribs <- vector("list", n_tasks)
    XtX <- matrix(0, p, p)
    for (k in seq_len(n_tasks)) {
      xi <- X_full[pairs[k, 1], ]; xj <- X_full[pairs[k, 2], ]
      contribs[[k]] <- outer(xi, xi) + outer(xj, xj)
      XtX <- XtX + contribs[[k]]
    }
    cur_det <- det(XtX)
    for (sweep in seq_len(n_sweep)) {
      for (k in seq_len(n_tasks)) {
        XtX_wo_k <- XtX - contribs[[k]]
        cand <- sample(n_adm, n_try)
        best_local_det <- cur_det; best_local_c <- contribs[[k]]
        for (cidx in cand) {
          ci <- admissible_idx[cidx, 1]; cj <- admissible_idx[cidx, 2]
          xci <- X_full[ci, ]; xcj <- X_full[cj, ]
          ck2 <- outer(xci, xci) + outer(xcj, xcj)
          d <- det(XtX_wo_k + ck2)
          if (d > best_local_det) { best_local_det <- d; best_local_c <- ck2 }
        }
        if (best_local_det > cur_det) {
          XtX <- XtX_wo_k + best_local_c
          contribs[[k]] <- best_local_c
          cur_det <- best_local_det
        }
      }
    }
    if (cur_det > best_det) best_det <- cur_det
  }
  best_det
}

# Grid of task counts from 20 to 144 (i.e. 40 to 288 profile evaluations,
# matching the profile-level grid one-for-one at 2 profiles per task).
n_task_grid <- unique(c(seq(20, 144, by = 5), 144))
n_random_reps <- 200

results_pair <- lapply(n_task_grid, function(nt) {
  d_opt <- doptimal_pairs(nt)^(1 / p) / (2 * nt)

  # Benchmark: n_random_reps sets of nt tasks drawn the way the survey
  # actually randomizes them -- profiles drawn independently and the pair
  # kept only if admissible, i.e. a uniform draw from admissible_idx.
  rand_deffs <- replicate(n_random_reps, {
    sel <- sample(n_adm, nt, replace = TRUE)
    pr <- admissible_idx[sel, , drop = FALSE]
    XtX <- matrix(0, p, p)
    for (k in seq_len(nt)) {
      xi <- X_full[pr[k, 1], ]; xj <- X_full[pr[k, 2], ]
      XtX <- XtX + outer(xi, xi) + outer(xj, xj)
    }
    detXtX <- det(XtX)
    if (is.na(detXtX) || detXtX <= 0) NA_real_ else detXtX^(1 / p) / (2 * nt)
  })

  data.frame(N_tasks = nt, D_optimal = d_opt, D_random = mean(rand_deffs, na.rm = TRUE))
}) |> bind_rows() |>
  mutate(gain_pct = 100 * (D_optimal / D_random - 1))

ggplot(results_pair, aes(x = N_tasks)) +
  geom_line(aes(y = D_optimal, color = "D-optimal")) +
  geom_line(aes(y = D_random, color = "Complete randomization")) +
  labs(x = "Number of tasks (pairs)", y = "D-efficiency (scaled)", color = NULL) +
  theme_minimal()
```

Of the `r format(choose(nrow(candidates),2), big.mark=",")` possible profile pairs, `r format(n_adm, big.mark=",")` (`r round(pct_admissible,1)`%) satisfy the restriction, so it rules out only a small corner of the pairing space. Consistent with that, the pair-level curves land almost on top of the profile-level ones: the optimal design is again essentially flat (`r round(min(results_pair$D_optimal),4)`–`r round(max(results_pair$D_optimal),4)`), and complete randomization under the restriction closes the gap from `r round(results_pair$gain_pct[results_pair$N_tasks==20],1)`% at N = 20 tasks (40 profile evaluations) to `r round(results_pair$gain_pct[results_pair$N_tasks==max(results_pair$N_tasks)],1)`% at N = `r max(results_pair$N_tasks)` tasks — practically identical to the unlabeled profile-level run, confirming that the relabeling changes nothing about the design's statistical properties.

The full candidate list of admissible pairs — `r format(n_adm, big.mark=",")` rows, one per admissible pair, with both profiles' attribute levels spelled out — is written to `output/conjoint-design/admissible_pairs.csv` for use in the survey implementation. A preview:

The back-of-envelope translation to respondents (at `r n_tasks` tasks per respondent, as above) gives the same order of saving as the profile-level check:

```{r}
#| label: tbl-deff-pair-envelope
#| tbl-cap: "Back-of-envelope respondents implied by the pair-level D-efficiency gain, at selected task-pool sizes"
#| echo: true
#| message: false
#| warning: false
envelope_pair <- results_pair |>
  filter(N_tasks %in% c(20, 50, 144)) |>
  mutate(
    ratio = D_optimal / D_random,
    respondents_random = round(n_respondents),
    respondents_D_optimal = round(n_respondents / ratio)
  ) |>
  select(N_tasks, ratio, respondents_random, respondents_D_optimal)

knitr::kable(
  envelope_pair, digits = c(0, 3, 0, 0),
  col.names = c("Task pool (N)", "Efficiency ratio", "Respondents (randomization)", "Respondents (D-optimal, implied)")
)
```

The conclusion is the same as at the profile level, now confirmed under the actual pairing restriction: the restriction itself costs almost nothing in achievable D-efficiency (94% of pairs remain usable), and the ceiling on what a D-efficient task design could save over complete randomization stays in the same modest range, at most on the order of `r round(100 * (1 - 1/envelope_pair$ratio[envelope_pair$N_tasks == 20]))`% fewer respondents. The same two caveats noted above still apply — the `cjpowR` baseline is not measured on identical terms, and this ignores respondent fixed effects and clustering — so this remains an exploratory bound, not a substitute for a simulation-based power calculation once pilot data are available.


### Implementation

- selection of the non-redundant pairs of profiles
- restrictions: the design imposes a single restriction, applied to the pair of profiles within a task rather than to individual attributes: the two profiles must differ on at least two of the six CARIN/NICER attributes (need, identity, control, effort, reciprocity, attitude). When a pair is generated, the six substantive attributes are drawn independently and the pair is retained only if it differs on two or more of them, otherwise it is redrawn. Sex is assigned afterward through the applicant's first name and does not enter the check, so the two profiles may share the same sex or not. The purpose is cognitive: a pair that is identical or differs on only one substantive attribute presents two near-indistinguishable applicants, yielding a task that carries little information about trade-offs.
- randomization of attributes order
- attention check
- inter reliability check

### Analysis considerations



## Attitudinal items @tomasurzuam

This section describes the second component of the survey instrument, complementing the conjoint design presented in the previous section. It first outlines the overall structure of the questionnaire. Then details the three batteries of items applied—market justice preferences, the meritocracy scale, and the deservingness (CARIN/NICER) scale—describing their conceptual origin, wording, and measurement specifications.

### Questionnaire Structure and Content

The questionnaire is structured around two main sections. First, a matching task is administered, in which respondents are presented with two profiles of people with different characteristics and, based on those characteristics, must allocate a sum of money to finance their college education. This section of the survey is explained in greater detail in the [previous chapter](https://jus-mer.github.io/survey-jusmer/documentation/docs/03-conjoint-desing.html). The second part of the measurement instrument is based on items regarding public opinion, perceptions, and/or preferences related to the market, merit, and deservingness, which are presented as multiple-choice questions. The following section provides a more in-depth look at the item scales that were used, their origin, and measurement specifications.

### Measurement Scales and Sources of Survey Items

The first wave of the survey contains the following sets of questions: Market Justice Preferences (1), Meritocracy Scale (2), and Deservingness (CARIN/NICER) Scale (3).

#### Market justice preferences

The “Market Justice Preferences” scale consists of three questions, which aim to determine the extent to which people consider it fair for access to and the quality of social services—such as education, health care, and pensions—to depend on market criteria. These questions originally come from the [International Social Survey Program](https://www.gesis.org/en/issp/data-and-documentation/social-inequality) (1999) and are included in the social inequality module. In this context, the scale first appeared in the 1999 version of the ISSP and has been included in all subsequent versions (2009 and 2019).

The question is phrased as follows: *Is it fair that in Chile, high-income individuals have access to better \_\_\_ than those with lower incomes?* The blank refers to the respective social service addressed by the scale.

The question is measured using a Likert scale ranging from “disagree” to “agree,” where (1) is “strongly disagree” (muy en desacuerdo) and (5) is “strongly agree” (muy de acuerdo).

#### Meritocracy scale

The meritocracy scale is based on a conceptual framework designed by @castillo_multidimensional_2023, which presents a multidimensional model for measuring meritocratic beliefs. This model distinguishes, first, between perceptions and preferences, where the former refers to the way people view the world, while the latter refers to how the world should function. Second, the model distinguishes between meritocratic and privilege-based perceptions and preferences; meritocratic factors relate to effort and talent, while the privilege factor considers inherited conditions such as family wealth and connections. This instrument was first implemented in a survey conducted between 2019 and 2020 as part of the [FONDECYT Regular project “The Moral Economy of Meritocracy and Redistributive Preferences”](https://jc-castillo.com/proyectos/posts/fondecyt-economiamoral/). Subsequently, this set of questions has been used in surveys targeting student and adult populations.

To better illustrate the items that make up the scale, the following table is provided (see @tbl-meritscale):

```{r}
#| label: tbl-meritscale
#| tbl-cap: "Meritocracy scale items"
#| echo: false
#| message: false
#| warning: false
library(here)
merit_scale <- read.csv(here::here("..", "input", "tbl", "merit-scale.csv"))
knitr::kable(merit_scale, col.names = c("Dimensions", "Factor", "Item english", "Item spanish"))
```

Each item on the scale is measured using a four-point agreement-disagreement scale, where (1) indicates “strongly disagree” and (4) indicates “strongly agree.” It is worth noting that this scale does not include any intermediate categories.

#### Deservingness scale

The merit scale is based on the conceptual and empirically validated proposal by @meuleman_welfare_2020, which allows for an empirical study of the normative criteria that citizens apply to determine who is eligible for social protection. The framework is built upon the operationalization of five central concepts:

-   Control: Refers to the perception of personal responsibility in the face of a situation of need.

-   Attitude: Assesses the beneficiary’s disposition toward society and their gratitude for the assistance received.

-   Reciprocity: Considers the beneficiary’s past or future contribution to the system, which implies an expectation of a return for the assistance people receive.

-   Identity: Assesses the moral boundaries of the community regarding its willingness to benefit another.

-   Need: Focuses on the urgency and severity of the beneficiary’s situation. In this case, need is distinguished from control because it refers to conditions that are beyond an individual’s control.

In addition, this survey includes the “effort” dimension based on the proposal by @knotz_recast_2022, who defines effort as the beneficiary’s active and present agency aimed at overcoming their situation of vulnerability or contributing in some way to society at the time they receive support. Based on these two models for measuring deservingness, this survey includes the following items (see @tbl-deservescale):

```{r}
#| label: tbl-deservescale
#| tbl-cap: "Deservingness scale items"
#| echo: false
#| message: false
#| warning: false
library(here)
deserve_scale <- read.csv(here::here("..", "input", "tbl", "deservingness-scale.csv"))
knitr::kable(deserve_scale, col.names = c("Model", "Dimension", "Item english", "Item spanish"))
```

The items are measured using a Likert scale ranging from “disagree” to “agree,” where (1) is “strongly disagree” (muy en desacuerdo) and (5) is “strongly agree” (muy de acuerdo).

## Socio-economic characterization (@tomasurzuam)
